---
title: "rRPMM"
author:
- name: Atsushi Fukushima
  affiliation: RIKEN Center for Sustainable Resource Science
  email: afukushima@gmail.com
date: "`r Sys.Date()`"
output:
  BiocStyle::html_document:
package: rRPMM
vignette: |
  %\VignetteIndexEntry{rRPMM}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

# Introduction
[RIKEN Plant Metabolome MetaDatabase (RPMM)](http://metabobank.riken.jp/) is 
used to provide integrated plant metabolome data generated by RIKEN. 
The database provides data in the bases of standardized metadata techniques 
including semantic web and Resource Description Framework (RDF). 
The rRPMM package is an accessor for RPMM.

# Installation

```{R}
# devtools::install_github("afukushima/rRPMM", build_vignettes = TRUE)
```

# Usage

```{r setup}
# suppressPackageStartupMessages(library(SPARQL))
# suppressPackageStartupMessages(library(rRPMM))
# suppressPackageStartupMessages(library(plotly))
# suppressPackageStartupMessages(library(dplyr))
# Sys.setenv(LANGUAGE="en_US.UTF-8") 

library(SPARQL)
library(rRPMM)
library(plotly)
library(dplyr)


res <- RPMM_numOfprojects_species()
resMat <- data.frame(gsub("@en", "", res$speciesLabel), res$callret.4)
colnames(resMat) <- c("Species", "num")

## for pie chart with plotly
resMat_1over <- resMat[resMat$num>1, ]
resMat_others <- resMat[resMat$num==1, ]
others <- list("Others", sum(resMat_others$num))
resMatfin <- rbind(resMat_1over, data.frame(Species="others", num="28"))

p <- plot_ly(resMatfin, labels = ~Species, values = ~num, type = 'pie') %>%
  layout(title = 'RPMM projects (Feb 19, 2020)',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, 
                      showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, 
                      showticklabels = FALSE))
p

```

# Getting all the raw data files in a Project (Accession #: RPMM0001)

```{r rawdata}
res <- RPMM_get_rawdata_files(project = "RPMM0001")
head(res$url)
```

# Session information {.unnumbered}

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
